
%A sense of unease, a distance to world around me, then a sudden lack of control, my body no longer obeys, soon the seizure will come. This is the feeling for some people who suffer from epileptic seizure, but for some there is no warning, no foreboding feeling, only a sudden seizure. Epilepsy is a neurological disorder that is affecting around 50 million people world wide 
%[https://www.who.int/news-room/fact-sheets/detail/epilepsy#:~:text=Epilepsy]
%. In this work we aim to provide that warning to those 50 million, thus improving their quality of life. We are not the first to atempt this, there has been a great deal of interest in the area of epileptic prediction and warning in recent years. 
%kolla den rapport som sammanställer

%As far as the current devices go they mostly aim at detecting sudden and unsuspected movement, whic 
%The system we propoce is that of a wearable hat, equiped whit electrodes that can detect EEG signals, whic then is runned through a Neural Network that detects the so called preictal state that precedes the epileptic seizure.

% Med figurer avses bilder, diagram, grafer mm. Det ska inte finnas ytterligare rubrik
% i figuren än den som står i figurtexten. Om ej egentillverkad skall källa anges samt
% tillstånd av ägare erhållas.
%
% Variabler skrivs kursivt både i ekvationerna och i brödtexten. Icke-variabler skrivs på vanligt sätt.
% Ekvationer betraktas som en del i texten. Ekvationsnummer ska skrivas längst ut till höger.

\subsection{Literature review}

\subsection{Epileptic seizures}
A (epileptic) seizure can be conceptualized as occurring when there is distortion of the normal balance between excitation (E) and
inhibition (I) in the brain (Stafstrom and Carmant, 2022, p. 3). In practice however this imbalnance can be expressed in a multidues of ways ranging from spasms, loss of consciousness and secondary injuries given from for example when repeatedly hitting hard surfaces with the head.
The seizure onset can be differantiated into four epileptic brain states, the Interictal state, the Preictal state, the Ictal state and the Post-ictal state.
The Interictal state is the "normal state" or when no seizure are present or on the way. The preictal state is just before seizure onset while The Ictal state is during the seizure onset. The Post-ictal is the state jus after the seizure and eventually fades out into a new Interictal state. 
There has been many studies discussing the existance of a preictal state but after the results of Lehnertz (2001), where changes just before seiuzure onset could be clearly seen, it has been regarded as a "proof of concept of the existence of a preictal state" Gadhoumi et al.(2015).
Seizure prediction cane be considered as early detection of the preictal state (Bou Assi et al, 2017, p. 1) which also is the goal of this project.

\subsection{Prediction}

\subsubsection{Dataset}

\subsubsection{Feature extraction}

\subsubsection{Prediction algoritm}
% Måste inte ha egen rubrik utan kan ingå i teorins löpande text.
% I fall teorikapitlet utelämnas ska litteraturstudie ingå i inledningen.
